Bioverse: Origins of Life

### 2024-07-10 src/tex/ms.tex
expand captions

\subsubsection{Selectivity of simulated transit surveys}
In Section~\ref{sec:results-semianalytical}, we demonstrated that the probability of obtaining true strong evidence for the hypothesis that life only originates on planets with a minimum past \gls{NUV} flux is sensitive to the distribution of sampled past \gls{NUV} fluxes, i.e., the selectivity of the survey (compare Figure~\ref{fig:semian_selectivity}).
%The maximum \gls{NUV} distribution of our generic transit survey is rather unimodal with a median around \SI{500}{\erg\per\second\per\centi\meter\squared} (see Figure~\ref{fig:nuv_distribution}), leading to a selectivity of roughly \var{selectivity_transit_volumelim}.
For both surveys targeting M dwarfs and those targeting FGK dwarfs, the maximum \gls{NUV} distribution is rather unimodal.
Applying the approach from Sect.~\ref{sec:results-semianalytical} of fitting a Beta function to the distribution, we find rather low selectivities (see Figure~\ref{fig:nuv_distribution}).
\begin{figure*}
    \script{nuv_distribution.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/nuv_distribution}
        \caption{Distribution of maximum past \gls{NUV} flux in transit surveys targeting FGK and M~stars, respectively. The best-fit beta distributions (gray) correspond to selectivities of $s_\mathrm{FGK} = $\var{selectivity_FGK} and $s_\mathrm{M} = $\var{selectivity_M}.}
        \label{fig:nuv_distribution}
    \end{centering}
\end{figure*}

@@

\begin{figure}
    \script{inhabited_aafo_nuv_thresh.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_aafo_nuv_thresh}
        \caption{Fraction of inhabited planets for different threshold \gls{NUV} fluxes under the UV hypothesis if the abiogenesis rate is \var{f_life}.}
        \label{fig:inhabited_aafo_nuv_thresh}
    \end{centering}
\end{figure}
Figure \ref{fig:inhabited_aafo_nuv_thresh} shows the fraction of inhabited planets under the UV hypothesis for different threshold \gls{NUV} fluxes and for a high abiogenesis rate of \var{f_life}.
This fraction decreases sharply with increasing threshold flux, as fewer planets receive sufficient \gls{NUV} flux for abiogenesis.
For the FGK sample, the fraction of inhabited planets drops at lower threshold fluxes than for the M dwarf sample.

>>>>

\subsubsection{Selectivity of simulated transit surveys}
In Section~\ref{sec:results-semianalytical}, we demonstrated that the probability of obtaining true strong evidence for the hypothesis that life only originates on planets with a minimum past \gls{NUV} flux is sensitive to the distribution of sampled past \gls{NUV} fluxes, i.e., the selectivity of the survey (compare Figure~\ref{fig:semian_selectivity}).
%The maximum \gls{NUV} distribution of our generic transit survey is rather unimodal with a median around \SI{500}{\erg\per\second\per\centi\meter\squared} (see Figure~\ref{fig:nuv_distribution}), leading to a selectivity of roughly \var{selectivity_transit_volumelim}.
For both surveys targeting M dwarfs and those targeting FGK dwarfs, the maximum \gls{NUV} distribution is rather unimodal.
Applying the approach from Sect.~\ref{sec:results-semianalytical} of fitting a Beta function to the distribution, we find rather low selectivities (see Figure~\ref{fig:nuv_distribution}).
\begin{figure*}
    \script{nuv_distribution.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/nuv_distribution}
        \caption{Distribution of maximum past \gls{NUV} flux in transit surveys targeting FGK and M~stars, respectively. The best-fit beta distributions (gray) correspond to selectivities of $s_\mathrm{FGK} = $\var{selectivity_FGK} and $s_\mathrm{M} = $\var{selectivity_M}. Red areas show inhabited planets for a threshold \gls{NUV} flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$ and an abiogenesis rate of $f_\mathrm{life} = \var{f_life}$.}
        \label{fig:nuv_distribution}
    \end{centering}
\end{figure*}

@@

\begin{figure}
    \script{inhabited_aafo_nuv_thresh.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_aafo_nuv_thresh}
        \caption{Fraction of inhabited planets for different threshold \gls{NUV} fluxes under the UV hypothesis if the abiogenesis rate is \var{f_life}. Shaded regions denote 90 percent confidence intervals of randomized sample generations.}
        \label{fig:inhabited_aafo_nuv_thresh}
    \end{centering}
\end{figure}
Figure \ref{fig:inhabited_aafo_nuv_thresh} shows the fraction of inhabited planets under the UV hypothesis for different threshold \gls{NUV} fluxes and for a high abiogenesis rate of \var{f_life}.
This fraction decreases sharply with increasing threshold flux, as fewer planets receive sufficient \gls{NUV} flux for abiogenesis.
For the FGK sample, the fraction of inhabited planets drops at lower threshold fluxes than for the M dwarf sample.
